---
title: "Mini Project 2"
author: "S18827"
date: "2024-05-18"
output: html_document
---

```{r}
data <- read_csv("../Data/Data/Algerian_forest_fires_dataset_UPDATE.csv", col_types = 'iiiiiidddddddcc')
data <- data %>%
  mutate(Classes = ifelse(Classes == "fire", 1, 0))

data <- na.omit(data) 
```
```{r}
x <- data[, 4:7]
summary(x)
```
```{r}
y <- data[, 8:14]
summary(y)
```

```{r}
library(tidyverse)
library(corrplot)
library(CCA)
library(CCP)
library(GGally)
library(psych)
library(skimr)
```


```{r}
data <- read_csv("../Data/led.csv")

data <- na.omit(data)
```


```{r}
x <- data %>% dplyr::select("Lifeexpectancy", "AdultMortality", "infantdeaths", "BMI", "under-fivedeaths", "HIV/AIDS")
skim(x)
x <- as.data.frame(scale(x))
```


```{r}
y <- data %>% dplyr::select("Alcohol", "HepatitisB", "Measles", "Polio", "Diphtheria", "Totalexpenditure", "percentageexpenditure")
skim(y)
y <- as.data.frame(scale(y))
```



```{r}
ggpairs(x)
```


```{r}
ggpairs(y)
```


```{r}
cov(x,y)
```
```{r}
correl <- matcor(x, y )
img.matcor(correl, type = 2)
```



```{r}
canonical_cor <- cc(x, y)
```

```{r}
# tests of canonical dimensions
rho <- canonical_cor$cor
## Define number of observations, number of variables in first set, and number of variables in the second set.
n <- dim(x)[1]
p <- length(x)
q <- length(y)

## Calculate p-values using the F-approximations of different test statistics:
p.asym(rho, n, p, q, tstat = "Wilks")
p.asym(rho, n, p, q, tstat = "Hotelling")
p.asym(rho, n, p, q, tstat = "Pillai")
p.asym(rho, n, p, q, tstat = "Roy")
```
Interpretation
For the first five canonical dimensions, all three tests (Wilks' Lambda, Hotelling-Lawley Trace, Pillai-Bartlett Trace) provide very small p-values (less than 0.05), indicating that these canonical correlations are significantly different from zero. This implies that there is a statistically significant relationship between the two sets of variables for the first five canonical dimensions.

However, for the sixth canonical dimension, the p-values are much larger (greater than 0.05), indicating that the sixth canonical correlation is not significantly different from zero. This means there is no statistically significant relationship between the sets of variables for the sixth canonical dimension.

Summary
First Five Canonical Dimensions: Significant relationships exist between the sets of variables.
Sixth Canonical Dimension: No significant relationship exists.
These results suggest that the first five canonical correlations capture significant relationships between the variable sets, while the sixth does not. This insight helps in determining how many canonical dimensions are necessary to capture the relationships between the two sets of variables effectively.





```{r}
# standardized psych canonical coefficients diagonal matrix of psych sd's
s1 <- diag(sqrt(diag(cov(x))))
s1 %*% canonical_cor$xcoef

# standardized acad canonical coefficients diagonal matrix of acad sd's
s2 <- diag(sqrt(diag(cov(y))))
s2 %*% canonical_cor$ycoef
```


```{r}
canonical_cor$cor
```

```{r}
canonical_cor[3:4]
```
```{r}
# compute canonical loadings
cc2 <- comput(x, y, canonical_cor)

# display canonical loadings
cc2[3:6]
```



