---
title: "S/18/827 Mini Project 2 CCA"
author: "S18827"
date: "2024-05-25"
output: html_document
---

```{r}
library(tidyverse)
library(ggplot2)
library(GGally)
library(psych)
library(CCA)
library(CCP)
library(dplyr)
library(corrplot)
```

A dataframe containing :

id
the farm identifier

size
the total area cultivated with rice, measured in hectares

status
land status, on of 'owner' (non sharecroppers, owner operators or leaseholders or both), 'share' (sharecroppers), 'mixed' (mixed of the two previous status)

varieties
one of 'trad' (traditional varieties), 'high' (high yielding varieties) and 'mixed' (mixed varieties)

bimas
bIMAS is an intensification program; one of 'no' (non-bimas farmer), 'yes' (bimas farmer) or 'mixed' (part but not all of farmer's land was registered to be in the bimas program)

seed
seed in kilogram

urea
urea in kilogram

phosphate
phosphate in kilogram

pesticide
pesticide cost in Rupiah

pseed
price of seed in Rupiah per kg

purea
price of urea in Rupiah per kg

pphosph
price of phosphate in Rupiah per kg

hiredlabor
hired labor in hours

famlabor
family labor in hours

totlabor
total labor (excluding harvest labor)

wage
labor wage in Rupiah per hour

goutput
gross output of rice in kg

noutput
net output, gross output minus harvesting cost (paid in terms of rice)

price
price of rough rice in Rupiah per kg

region
one of 'wargabinangun', 'langan', 'gunungwangi', 'malausma', 'sukaambit', 'ciwangi'

```{r}
data <- read_csv("../Data/Data/RiceFarms.csv")
data <- data %>%
  mutate(status = case_when(
                  status == "owner" ~ 1,
                  status == "share" ~ 2,
                  status == "mixed" ~ 3,
                  TRUE ~ NA_real_),
        varieties = case_when(
                    varieties ==  "trad" ~ 1,
                    varieties == "high" ~ 2,
                    varieties == "mixed" ~ 3,
                    TRUE ~ NA_real_),
        bimas = case_when(
                bimas == "no" ~ 0,
                bimas == "yes" ~ 1,
                bimas == "mixed" ~ 3,
                TRUE ~ NA_real_)
  )
```


```{r}
skimr::skim(data)


data <- data %>% dplyr::select(-rownames, -id, -region) 
```

```{r}
set1 <- dplyr::select(data, goutput, noutput, price)
skimr::skim(set1)

set2 <- dplyr::select(data, seed, urea, phosphate, pesticide, pseed, purea, pphosph, hiredlabor, famlabor, totlabor, wage) 
skimr::skim(set2)

```

```{r}
canonical_cor <- cc(set1, set2)

canonical_cor$cor
canonical_cor$xcoef
canonical_cor$ycoef
```
```{r}
# compute canonical loadings
cc2 <- comput(set1, set2, canonical_cor)

# display canonical loadings
cc2[3:6]
```

```{r}
# tests of canonical dimensions
rho <- canonical_cor$cor
## Define number of observations, number of variables in first set, and number of variables in the second set.
n <- dim(set1)[1]
p <- length(set1)
q <- length(set2)

## Calculate p-values using the F-approximations of different test statistics:
p.asym(rho, n, p, q, tstat = "Wilks")
p.asym(rho, n, p, q, tstat = "Hotelling")
p.asym(rho, n, p, q, tstat = "Pillai")
p.asym(rho, n, p, q, tstat = "Roy")
```


```{r}
# standardized psych canonical coefficients diagonal matrix of psych sd's
s1 <- diag(sqrt(diag(cov(set1))))
s1 %*% canonical_cor$xcoef

# standardized acad canonical coefficients diagonal matrix of acad sd's
s2 <- diag(sqrt(diag(cov(set2))))
s2 %*% canonical_cor$ycoef
```

```{r}
m <- cor(data)
m
corrplot(m, method = 'circle')
colnames(data)
```

